---
title: "BLT_9.5"
author: "Manjula Kottegoda"
date: "July 13, 2016"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preparing Financial Data

Assignment

You will be assigned to find a series that is less volatile than the S&P 500, the other half a series that is more volatile.

Here we are using Agios Pharmaceuticals Inc. AGIO

### 1. Load require packages and download the data for the given stock

```{r}
require('tseries')
require('fpp') 
#Download data series - get.hist.quote gets historical data of the given ticker symbol
# Here we are using Agios Pharmaceuticals Inc. AGIO
SNPdata <- get.hist.quote('AGIO',quote="Close")
#Get count to see if download was successful
length(SNPdata)
```

### 2. Calculate log returns.
```{r}
# Calculate log returns of same dataset
SNPret <- log(lag(SNPdata)) - log(SNPdata)
length(SNPret)
```



### 3. Calculate volatility measure.
```{r}
# Calculate Volatility for 250 trading days
# 250 is the number of trading days and multiplication by 100 to get  as a percentage 
SNPvol <- sd(SNPret) * sqrt(250) *100  
```


### 4. Calculate volatility over entire length of series for three different decay factors.
```{r}
# Function to create volatility in a contiouus loopback
# Author: Dr Monnie McGee
Vol <- function(d, logrets){
      var = 0
      lam = 0
      varlist <- c()
      for (r in logrets){
        
        lam = lam * (1 - 1/d) +1 
        
        var = (1 - 1/lam)*var+ (1/lam)*r^2
            varlist <- c(varlist, var)
      }
    sqrt(varlist)
}

# Calculating for 3 decay factors
volest <- Vol(10, SNPret)     #Weight .1
volest2 <- Vol(30, SNPret)    #Weight .33
volest3 <- Vol(100, SNPret)   #Weight .99

```




### 5. Plot the results, overlaying the volatility curves on the data.

```{r}
plot(volest,type='l') # volatility of the stock
lines(volest2,type='l', col = 'red')
lines(volest3,type='l', col = 'blue') # smooth with higher weight
```


This is a graph of the volatility not the stock price. High peaks correspond to high fluctuations on the price of the particular stock.
